Optimal (Multiway) Spatial Joins

### 2024-05-26 msj.tex
yufei

Let $P'$ be the set of remaining points in $P$ after the aforementioned removal. Next, for each $j \in [k-1]$, solve the reporting version of Problem $\mathscr{A}$ by feeding $P'$ and $R_j$ as the input. Doing so produces, for each point $p \in P'$, $\contained_{R_j}(p)$, which --- as defined in \eqref{eqn:contained} (noticing that $p$ is a degenerated ``horizontal segment'') --- is the set of rectangles in $R_j$ covering $p$. By the discussion in Section~\ref{sec:bricks}, the total cost of this step is bounded by
\myeqn{
    O\Big(kn \log n + \sum_{j \in [k-1]} \sum_{p \in P'} |\contained_{R_j}(p)| \Big). \label{eqn:ksj:cat1:help1}
}

We are now ready to generate $\J^\cat_k$. Take any point $p \in P'$, let $r_k \in R_k$ be the rectangle with $p$ as the top-left corner. For every $(k-1)$-tuple 
\myeqn{
    (r_1, ..., r_{k-1}) \in \contained_{R_1}(p) \times ... \times \contained_{R_{k-1}}(p) \label{eqn:ksj:cat1:help2}
}

>>>>

Let $P'$ be the set of remaining points in $P$ after the aforementioned removal. Next, for each $j \in [k-1]$, solve the reporting version of Problem $\mathscr{A}$ by feeding $P'$ and $R_j$ as the input. Doing so produces, for each point $p \in P'$, $\contained_{R_j}(p)$, which --- as defined in \eqref{eqn:contained} (noticing that $p$ is a degenerated ``horizontal segment'') --- is the set of rectangles in $R_j$ covering $p$. By the discussion in Section~\ref{sec:bricks}, the total cost of this step is bounded by
\myeqn{
    O\Big(kn \log n + \sum_{p \in P'} \sum_{j \in [k-1]} |\contained_{R_j}(p)| \Big). \label{eqn:ksj:cat1:help1}
}

We are now ready to generate $\J^\cat_k$. Take any point $p \in P'$, let $r_k \in R_k$ be the rectangle with $p$ as the top-left corner. For every $(k-1)$-tuple 
\myeqn{
    (r_1, ..., r_{k-1}) \in \contained_{R_1}(p) \times ... \times \contained_{R_{k-1}}(p) \label{eqn:ksj:cat1:help2}
}
we add $(r_1, ..., r_{k-1}, r_k)$ to $\J^\cat_k$. Performing the above for all $p \in P'$ correctly generates the whole $\J^\cat_k$ in $O(1 + |\J^\cat_k|)$ time. The way $P'$ is computed ensures that $\contained_{R_j}(p)$ is non-empty for all $j \in [k-1]$. Hence, $\sum_{j \in [k-1]} |\contained_{R_j}(p)|$ is bounded by $\prod_{j \in [k-1]} |\contained_{R_j}(p)|$. This implies that \eqref{eqn:ksj:cat1:help1} is bounded by $O(kn \log n + k \cdot |\J^\cat_k|)$.
